Probabilistic Topic Modelling for Spatial Smoothing in Mass Spectrometry Imaging

### 2016-12-12 docs/MSci_proposal/mprop.tex
Work plan: deliverables. Initial draft.

% Dates
% - Non-continuous
% - Estimations
\par The outlined tasks will not be necessarily executed in sequential manner. For some of the tasks, we will use parallel approach as given in Figure \ref{fig:gantt} below.

@@

\ganttgroup{Documentation/Presentation}{2}{15} \\
\ganttbar{Reports}{2}{11} \\
\ganttbar{Dissertation}{10}{15} \ganttnewline
\ganttbar[
=TBA
]{Presentation}{12}{14}

@@

% Code
% Dissertation
\subsection{Deliverables}

% Conclusion
\par

>>>>

% Dates
% - Non-continuous
% - Estimations
\par The outlined tasks will not be necessarily executed in sequential manner. For some of the tasks, we will use the parallel approach as given in Figure \ref{fig:gantt} below.

@@

\ganttgroup{Documentation/Presentation}{2}{15} \\
\ganttbar{Reports}{2}{11} \\
\ganttbar{Dissertation}{10}{15} \ganttnewline
\ganttbar{Presentation}{12}{14}

@@

\subsection{Deliverables}

% - Successful/Unsuccessful
% - Model in Python 
% -- 2/3 objectives
% - Dissertation
% - Presentation
\par The deliverables of the project will depend on the outcome of the initial hypothesis -- `the degeneracies of MSI data sets can be detected using LDA-like models'. Nevertheless, in any of the project's outcomes, we will provide the following deliverables: the presentation; the dissertation; and the spatial smoothing model, which will be written in Python. However, the main project's contribution to the research in MSI will depend on the results: if the model displays an improvement in performance, then we could utilise the model in pre-processing MSI data sets; in the case of unsuccessful outcome, we would assess the techniques used and provide details on why the model does not work. Both outcomes would bring the motivation for further research in improving MSI data sets: the successful outcome would bring attention to the applicability of LDA-like models; the unsuccessful outcome would suggest the need of a different perspective required to tackle the issue of noise.
